---
title: "DDS - Live Session 1"
author: "CDHolmes"
date: "10/30/2021"
output: html_document
---


## Control Parameters
```{r}
population = 10000000 # population size
simulations = 10000
sample_size = 50
df = 2
```

## Chi-squared distribution
```{r}
chi_sqr_dist = rchisq(population, df)
chi_sqr_dist

hist(chi_sqr_dist, col = c("#ff6666"), xlab = NULL, main = paste("Chi-Square Distribution: df = ", df))
mean(chi_sqr_dist)
sd(chi_sqr_dist)
```

## Data Holders
```{r}
xbar_holder1 = numeric(simulations) # This will hold all the sample means for the first distribution.
```

## Simulate and Store
```{r}
for (i in 1:simulations)
{
  sample1 = sample(chi_sqr_dist,sample_size)
  xbar1 = mean(sample1)
  xbar_holder1[i] = xbar1
}
```

## Display the distribution of sample means (plot a histogram of the sample means)
```{r}
hist(xbar_holder1, col = c("#ff9966"), main = paste("Distribution of the sample mean: n = ", sample_size), xlab = "Dist Sample Means", xlim = c(-4,4))
```

## summary statistics of the distribution of the simulated sample means.
```{r}
mean(xbar_holder1)
sd(xbar_holder1)
```



# Beach Comber T-Test

## Parameters
```{r}
ages = c(25,19,37,29,40,28,31)
n = length(ages)
alpha = .05
```

## Step 1 - Claim: mean age of the distribution of Comber patrons is <> 21
##  Ho: mu = 21
##  Ha: mu <> 21
```{r}
ho = 21
```

## Step 2
```{r}
critval = qt(alpha/2 , n - 1, lower.tail = FALSE)
critval

```

## Step 3 - Critical Value
```{r}
ttest = t.test(ages, mu = ho, alt = "two.sided", conf= 1 - alpha)
tstat = ttest$statistic
tstat
```

## Step 4 - p-value
```{r}
pval = ttest$p.value
pval
```

## Step 5 - Reject or fail to reject Ho
```{r}
ttest
```

## Step 6
## There is enough evidence to suggest the true mean of the distribution of 
## Comber patrons is not equal to 21 (p-value = 0.01622)

