---
title: "DDS Live Session 2"
author: "CDHolmes"
date: "11/7/2021"
output: html_document
---

# Packages
```{r}
library(ggplot2)
library(magrittr)
library(dplyr)
library(plotly)
library(tidyr)
```

# Data Import from csv
```{r}
bball_players <- read.csv("C:/Users/corey/OneDrive/Documents/School/Classes/Doing Data Science/MSDS_6306_Doing-Data-Science/Unit 2/PlayersBBall.csv", header = TRUE) # headers are included in data
```

# 1: Visually represent the number of players in each position.
```{r}
bball_players %>% ggplot(aes(x = position, fill = position)) +
  geom_bar() +
  xlab("Position") +
  ylab("Count") +
  ggtitle("Player Count by Position") +
  theme_minimal()
```

# 2: Use the dataset to visually investigate the distribution of the weight of 
# centers (C) is greater than the distrbution of the weight of forwards (F).
```{r}
# Histogram
w <- bball_players %>%
  filter(position == "C" | position == "F") %>%
  ggplot(aes(fill = position)) +
  geom_histogram(aes(x = weight)) +
  xlab("Weight(lbs)") +
  ylab("Count") +
  xlim(100, 400) +
  ggtitle("Center & Forward Weight Distribution") +
  facet_wrap(~position) +
  theme_minimal()
ggplotly(w)

# Box Plot
w_2 <- bball_players %>%
  filter(position == "C" | position == "F") %>%
  ggplot(aes(fill = position)) +
  geom_boxplot(aes(x = position, y = weight)) +
  xlab("Position") +
  ylab("Weight(lbs)") +
  ggtitle("Center & Forward Weight Distribution") +
  theme_minimal()
ggplotly(w_2)
```

# 3: Use the dataset to visually investigate if the distribution of the height of 
# centers (C) is greater than the distrbution of the height of forwards (F)
```{r}
# Transform Height to numeric
bball_new <- bball_players %>%
  separate(height, c("feet", "inch"), sep = "-", fill = "right") %>%
  mutate(inches = 12 * as.numeric(feet) + as.numeric(inch))

# Set x scale based on min and max height values
min_height <- min(bball_new$inches, na.rm = TRUE)
max_height <- max(bball_new$inches, na.rm = TRUE)

# Plot histogram of Height by Position

## Histogram
h <- bball_new %>%
  filter(position == "C" | position == "F") %>%
  ggplot(aes(x = inches, fill = position)) +
  geom_histogram() +
  facet_wrap(~position) +
  xlab("Height(in)") +
  ylab("Count") +
  xlim(min_height, max_height) +
  ggtitle("Center & Forward Height Distribution") +
  theme_minimal()
ggplotly(h)

## Box Plot
h_2 <- bball_new %>%
  filter(position == "C" | position == "F") %>%
  ggplot(aes(fill = position)) +
  geom_boxplot(aes(x = position, y = weight)) +
  xlab("Position") +
  ylab("Weight(lbs)") +
  ggtitle("Center & Forward Weight Distribution") +
  theme_minimal()
ggplotly(h_2)
```

# 4: Use the dataset to visually investigate if the distribution of height is 
# different between any of the positions.
```{r}
# Plot histogram of Height by Position

## Histogram - facet_wrap
h_3 <- bball_new %>%
  ggplot(aes(x = inches, fill = position)) +
  geom_histogram() +
  facet_wrap(~position) +
  xlab("Height(in)") +
  ylab("Count") +
  xlim(min_height, max_height) +
  ggtitle("Center & Forward Height Distribution") +
  theme_minimal()
ggplotly(h_3)

## Box Plot
h_4 <- bball_new %>%
  ggplot(aes(x = position, y = inches, fill = position)) +
  geom_boxplot() +
  xlab("Position") +
  ylab("Height(in)") +
  ggtitle("Center & Forward Height Distribution") +
  theme_minimal()
ggplotly(h_4)
```

# 5: Use the dataset to investigate how the player's height is related to the 
# player's weight. How does height change as the weight changes?
```{r}
# Scatter Plot
bball_new %>% ggplot(aes(x = inches, y = weight)) +
  geom_point(position = "jitter") +
  geom_smooth(method = "lm") +
  xlab("Height(in)") +
  ylab("Weight(lbs)") +
  ggtitle("Height v. Weight") +
  theme_minimal()

# Smooth
bball_new %>% ggplot(aes(x = inches, y = weight)) +
  geom_smooth(color = "blue") +
  xlab("Height(in)") +
  ylab("Weight(lbs)") +
  ggtitle("Height v. Weight") +
  theme_minimal()
```

# 6: Is there any difference in the relationship between height and weight between
# positions? Are height and weight related differently for different positions?
```{r}
## Single scatter plot view
bball_new %>% ggplot(aes(x = inches, y = weight)) +
  geom_point(aes(color = position), position = "jitter") +
  geom_smooth(method = "lm") +
  xlab("Height(in)") +
  ylab("Weight(lbs)") +
  ggtitle("Height v. Weight by Position") +
  theme_minimal()

## Single smooth
bball_new %>% ggplot(aes(x = inches, y = weight)) +
  geom_smooth(aes(color = position)) +
  xlab("Height(in)") +
  ylab("Weight(lbs)") +
  ggtitle("Height v. Weight by Position") +
  theme_minimal()

## Facet scatter plot view
bball_new %>% ggplot(aes(x = inches, y = weight)) +
  geom_point(aes(color = position), position = "jitter") +
  geom_smooth(method = "lm") +
  facet_wrap(~position) +
  xlab("Height(in)") +
  ylab("Weight(lbs)") +
  ggtitle("Height v. Weight by Position (Facet)") +
  theme_minimal()

## Facet smooth
bball_new %>% ggplot(aes(x = inches, y = weight)) +
  geom_smooth(aes(color = position)) +
  facet_wrap(~position) +
  xlab("Height(in)") +
  ylab("Weight(lbs)") +
  ggtitle("Height v. Weight by Position (Facet)") +
  theme_minimal()
```

# A historian would like to investigate the claim that the heights of players 
# have increased over the years. Analyze this claim graphically / visually.
```{r}
# I chose to use 'year_start' to compare heights over 'year_end' because
# waiting till the end of a players career to consider their heights will skew
# the data due to different career lengths.

## Bar Chart w/ smooth
m_height <- bball_new %>% ggplot(aes(x = year_start, y = inches)) +
  geom_bar(stat = "summary", fill = "#396e75") +
  geom_smooth(method = "lm") +
  xlab("Star Year") +
  ylab("Height(in)") +
  ggtitle("League Mean Height Over Time") +
  theme_minimal()
ggplotly(m_height)

## Scatter Plot w/ smooth
m_height2 <- bball_new %>% ggplot(aes(x = year_start, y = inches)) +
  geom_point(stat = "summary", fill = "#396e75") +
  geom_smooth(method = "lm") +
  xlab("Star Year") +
  ylab("Height(in)") +
  ggtitle("League Mean Height Over Time") +
  theme_minimal()
ggplotly(m_height2)
```

# Create a 3D plot of height vs. weight vs. year and color code the points by 
# position.
```{r}
d <- plot_ly(bball_new, x = ~year_start, y = ~weight, z = ~inches, color = ~position) %>%
  add_markers() %>%
  layout(scene = list(
    xaxis = list(title = "Start Year"),
    yaxis = list(title = "Weight"),
    zaxis = list(title = "Height")
  ))
d
```

# Use one of the 50 best plots to visualize some aspects of the data and 
# provide at least one insight. 
```{r}
# Find last
start_max <- max(bball_new$year_start, na.rm = TRUE)
start_range <- 40

bp <- bball_new %>%
  filter(year_start >= (start_max - start_range) & year_start <= start_max) %>%
  ggplot(aes(x = as.character(year_start), y = inches)) +
  xlab("Start Year") +
  ylab("Height(in)") +
  ggtitle("Player Height Summary Past 40 years") +
  geom_boxplot(fill = c("#3399CC")) +
  theme_minimal()
ggplotly(bp)
```

# Education Income

# Visually test the claim that the distribution of incomes increase 
#(mean or median) as the educatin level rises.
```{r}
# Datat Import
edu_income <- read.csv("C:/Users/corey/OneDrive/Documents/GitHub/MSDS_6306_Doing-Data-Science/Unit 2/Education_Income.csv", header = TRUE) # headers are included in data

# Set Education Level Order
edu_income$Educ <- factor(edu_income$Educ, levels = c("<12", "12", "13-15", "16", ">16"))

# Bar Chart
edu_income %>% ggplot(aes(x = Educ, y = Income2005)) +
  geom_bar(stat = "summary") +
  xlab("Education Level") +
  ylab("Mean Income") +
  ggtitle("Mean Income by Education Level") +
  theme_minimal()

# Code from class
bymedian <- with(edu_income, reorder(Educ, Income2005, median))
edu_income$ord_educ = bymedian
edu_income %>% ggplot(aes(x = ord_educ, y = Income2005, fill = ord_educ)) +
  geom_boxplot() +
  ggtitle("Income v. Education Level") +
  xlab("Income") +
  ylab("Education Level")
```
