# Packages
```{r}
library(ggplot2)
library(magrittr)
library(dplyr)
library(tidyverse)
library(GGally)
library(nycflights13)
library(naniar)
library(plotly)
library(stringr)
```

# Part 1

```{r}
# Import Data
fifa <- read.csv("C:/Users/corey/OneDrive/Documents/GitHub/MSDS_6306_Doing-Data-Science/Unit 3/FIFA Players.csv", header = TRUE)
```

## Question 1
## Using the FIFA player data set, filter the data set to create a Dataframe
## that has just the Left Midfilders (LM) and Left Forwards (LF)
```{r}
fifa_left <- fifa %>% filter(Position == "LM" | Position == "LF")
```

## Question 2
## Use Ggally and ggpairs() and the dataset you created above, to plot the 
## categorical variable Position (LM and LF), versus the continuous variables 
## Acceleration and Agility.
```{r}
fifa_left %>%
    select(Acceleration, Agility, Position) %>%
    ggpairs(aes(color = Position))
```

## Question 3
## Given the plot above, what relationships do you see?
```{r}
# Agility and Acceleration appear to have a positive linear coorelation.
# LF appear to be more agile.
```

## Question 4
## Test if the mean agaility rating of left midfielders (LM) is different than
## that of the left forwards (LF). Perform a 6 step t-test to test the 
## difference of these means.
```{r}
# Variables
alpha <- .05
fifa_agil <-
    fifa_left %>%
    select(Position, Agility)

## n values
n <- fifa_agil %>%
    select(Position) %>%
    group_by(Position) %>%
    summarize(count = n())
n1 <- n %>%
    filter(Position == "LF") %>%
    select(count)
n2 <- n %>%
    filter(Position == "LM") %>%
    select(count)

# Step 1
## ho: mu1 = mu2 # nolint
## ha: mu1 <> mu2 # nolint

# Step 2
## Critical Value
critval <- qt(alpha / 2, n1$count + n2$count - 2, lower.tail = FALSE)
critval

# Step 3
## t-value

## Assuming unequal variance
ttest <- t.test(Agility ~ Position, data = fifa_agil)
tstat <- ttest$statistic
tstat

## Assuming equal variance
ttest2 <- t.test(Agility ~ Position, data = fifa_agil, var.equal = TRUE)
tstat2 <- ttest$statistic
tstat2


# Step 4
## p-value
pval <- ttest$p.val
pval

pval2 <- ttest2$p.val
pval2

# Step 5
# Reject/Fail to reject Ho
## Fail to reject Ho
ttest
ttest2

# Step 6
## There is not enough evidence to suggest that the mean agility rating of
## Left Midfilders is different from Left Forwards (p = 0.06314)
```

## Question 5
## Are the assumptions of this test reasonably met?
## Do you think the sampling distribution of sample means will be reasonably normal?
## Does there look like there is significant visual evidence to suggest the standard deviations are different?
```{r}
# Histograms of each Position split up because the number of LM makes it
# difficult to see LF charts when put on the same axis
fifa_agil %>%
    filter(Position == "LF") %>%
    ggplot(aes(x = Agility)) +
    geom_histogram(fill = "#6060d8")

fifa_agil %>%
    filter(Position == "LM") %>%
    ggplot(aes(x = Agility)) +
    geom_histogram(fill = "red")

# Box Plots to evaluate spread
box <-
    fifa_agil %>%
    ggplot(aes(x = Position, y = Agility, fill = Position)) +
    geom_boxplot()
ggplotly(box)
```
 
# Part 2

## Select/create at least 2 categorical variables and select two continuous 
## variables and perform an EDA.  Also, at least one of the categorical 
## variables should be created from a continuous variable (using the cut() 
## function).

## Nationality, Wages, Position, Age, Overall

## Players by Nationality
## Overall by Nationality
## Highest Wages by Position
## Most valued Stat by position based on compensation of position
```{r}
# Create player score categories
overall_factor <-
  cut(fifa$Overall,
      breaks = c(1, 70, 80, 90, 95, 100),
      labels = c("D", "C", "B", "A", "S"))

# Transfor Wage, select columns, and create categories for Position
fifa_new <-
  fifa %>%
  select(Nationality, Wage, Position, Age, Overall) %>%
  mutate(
    Wage = as.numeric(str_remove_all(Wage, "[€K]")),
    Overall_Fact = overall_factor,
    Position2 = case_when(
      Position == "ST" ~ "Offense",
      Position == "RF" ~ "Offense",
      Position == "LF" ~ "Offense",
      Position == "CF" ~ "Offense",
      Position == "RS" ~ "Offense",
      Position == "LS" ~ "Offense",
      Position == "RW" ~ "Offense",
      Position == "LW" ~ "Offense",
      Position == "RCM" ~ "Mid",
      Position == "LCM" ~ "Mid",
      Position == "RDM" ~ "Mid",
      Position == "LDM" ~ "Mid",
      Position == "CAM" ~ "Mid",
      Position == "CDM" ~ "Mid",
      Position == "LAM" ~ "Mid",
      Position == "RAM" ~ "Mid",
      Position == "LM" ~ "Mid",
      Position == "RM" ~ "Mid",
      Position == "CM" ~ "Mid",
      Position == "RCB" ~ "Defense",
      Position == "LCB" ~ "Defense",
      Position == "LB" ~ "Defense",
      Position == "RB" ~ "Defense",
      Position == "CB" ~ "Defense",
      Position == "RWB" ~ "Defense",
      Position == "LWB" ~ "Defense",
      Position == "GK" ~ "Golie",
      TRUE ~ "Unmatched"
    )
  )

# Ggpairs
fifa_new %>%
  select(Position2, Overall_Fact, Age, Wage) %>%
  ggpairs()

# Player count by Position
d <- fifa_new %>%
  ggplot(aes(x = Position2, fill = Position2)) +
  geom_bar() +
  xlab("Position") +
  ylab("Count") +
  ggtitle("Player Counts by Position")
ggplotly(d)

# Wages vs. Player Score
fifa_new %>%
  ggplot(aes(x = Overall_Fact, y = Wage)) +
  geom_boxplot(aes(fill = Overall_Fact)) +
  xlab("Player Grade") +
  ylab("Wage") +
  ggtitle("Wage vs. Player Score") +
  theme_minimal()


# Player Score vs. Age
fifa_new %>%
  ggplot(aes(x = Overall_Fact, y = Age)) +
  geom_boxplot(aes(fill = Overall_Fact)) +
  xlab("Player Grade") +
  ylab("Age") +
  ggtitle("Age vs. Player Score") +
  theme_minimal()


# Position vs. Age
fifa_new %>%
  ggplot(aes(x = Position2, y = Age)) +
  geom_boxplot(aes(fill = Position2)) +
  xlab("Position") +
  ylab("Age") +
  ggtitle("Age vs. Position") +
  theme_minimal()


# Wage vs. Age with Player Score color
fifa_new %>%
  ggplot(aes(x = Wage, y = Age, color = Overall_Fact)) +
  geom_point() +
  xlab("Wage") +
  ylab("Age") +
  ggtitle("Wage vs. Age") +
  theme_minimal()

# Top 10 Nations by Player Count
fifa %>%
  select(Nationality) %>%
  group_by(Nationality) %>%
  summarise(count = n()) %>%
  top_n(10, count) %>%
  arrange(desc(count)) %>%
  ggplot(aes(x = reorder(
    Nationality, count,
    function(x) -x
  ), y = count)) +
  geom_bar(stat = "identity") +
  xlab("Nationality") +
  ylab("Count") +
  ggtitle("Top 10 Nations by Count") +
  theme_minimal()

# Top 10 Nations by Mean Player Score
fifa %>%
  select(Overall, Nationality) %>%
  group_by(Nationality) %>%
  summarise(avg_overall = mean(Overall)) %>%
  top_n(10, avg_overall) %>%
  arrange(desc(avg_overall)) %>%
  ggplot(aes(x = reorder(
    Nationality, avg_overall,
    function(x) -x
  ), y = avg_overall)) +
  geom_bar(stat = "identity") +
  xlab("Nationality") +
  ylab("Average Overall") +
  ggtitle("Top 10 Nations by Overall") +
  theme_minimal()
```