---
title: "Unit 2"
author: "CDHolmes"
date: "11/7/2021"
output: html_document
---
### GOAL: Assess if there is evidence that the relationship between city and highway mpg is different based on the drive of the car (4 wheel, front, or rear)

```{r}
## Create a scatter plot with just the points.
mpg %>% ggplot(aes(x = hwy, y = cty)) + geom_point()

## Create a plot with just the smoothed line.
mpg %>% ggplot(aes(x = hwy, y = cty)) + geom_smooth()

## Create a plot that has a different line for each level of drive(drv).
mpg %>% ggplot(aes(x = hwy, y = cty,linetype = drv)) + geom_smooth()

## Create a plot that has the smoothed line and the points and desgnate the
## type of drive by color... in both the line and the points.
mpg %>% ggplot(aes(x = hwy, y = cty, color = drv)) + geom_smooth() + geom_point()
  
## Create a plot that has the points and the smoothed line but the color
## designates the class of the car and the lines are differentiated by the 
## drive variable.
mpg %>% ggplot() + geom_point(mapping = aes(x = hwy, y = cty, color = class)) +
geom_smooth(mapping = aes(x = hwy, y = cty, linetype = drv, color = drv))


```

### Juding from the Loess curves, there is not sufficient evidence to suggest the relationship between highway and city mpg is different based on the drive of the car.

### Titles
```{r}
mpg %>% ggplot(aes(x = hwy, y = cty, color = drv)) + geom_smooth() + geom_point() + ggtitle("City v. Highway MPG") + xlab("Highway") + ylab("City")
```

## Facet 
```{r}
mpg %>% ggplot() + geom_point(mapping = aes(x = hwy, y = cty, color = class)) +
geom_smooth(mapping = aes(x = hwy, y = cty, linetype = drv)) + facet_wrap(~class)

mpg %>% ggplot() + geom_point(mapping = aes(x = hwy, y = cty, color = drv)) +
geom_smooth(mapping = aes(x = hwy, y = cty, linetype = drv)) + facet_grid(drv~class)

mpg %>% ggplot(aes(fill = drv)) + geom_histogram(mapping = aes(x = cty)) + facet_grid(drv~class)

```

### Bar Charts - Statistical Transformations/Derived Features
```{r}
mpg %>% ggplot(aes(x = class)) + geom_bar(stat = "count") # Default stat is 'count'

mpg %>% ggplot(aes(x = class, y = class)) + geom_bar() # Produces an error because it's not supposed to have a 'y' defined

mpg %>% ggplot(aes(x = class, y = cty)) + geom_bar(stat = "identity")
```


### Positions
```{r}
mpg %>% ggplot(aes(x = class, fill = drv)) + geom_bar(position = "stack") # Default position is 'stack'

mpg %>% ggplot(aes(x = class, fill = drv)) + geom_bar()

mpg %>% ggplot(aes(x = class, fill = drv)) + geom_bar(position = "dodge")

mpg %>% ggplot(aes(x = class, fill = drv)) + geom_bar(position = "fill")
```








